Phylogenetics and the human microbiome.

### 2013-04-02 sbreview.tex

We will begin by introducing the results of recent research.
There have been hundreds of papers concerning the human microbiome.
It is not our desire to survey all of these.
Rather, our idea is to highlight areas that may be of particular interest for the phylogenetics community by potentially having wider applications or by being areas for future exploration.
Please note that many of the methods and issues described in this paper will be equally useful for microbial ecology in general, but by narrowing our scope we were able to keep our paper within reasonable size limits.

Major finding: dynamic in terms of representation but diverse in terms of function.

@@

Major finding: antibiotics.
\cite{dethlefsen2008pervasive,dethlefsen2011incomplete,jakobsson2010short,jernberg2007long}

Enterotypes discussion.

@@

\cite{ley2006microbial}
Microbial ecology: human gut microbes associated with obesity

@@

There has been a shift from interest in community dynamics to fine-scale interactions between host and immune system.
\cite{wylie2012sequence}
\cite{chen2012associating}

>>>>

We will begin by introducing the results of recent research.
% There have been hundreds of papers concerning the human microbiome, and it is not our desire to survey all of these.
% Rather, our idea is to highlight areas that may be of particular interest for the phylogenetics community by potentially having wider applications or by being areas for future exploration.
% Please note that many of the methods and issues described in this paper will be equally useful for microbial ecology in general, but by narrowing our scope we were able to keep our paper within reasonable size limits.

The human microbiome has remarkable metabolic potential.
cite qin paper, and follow up

The microbiome is dynamic in terms of representation but apparently constant in terms of function.
cites

Human microbiome is spatially organized.
cite segre,

Inter-individual versus intra-individual variation.

16s surveys have shown that antibiotics fundamentally disturb microbial communities, resulting in an effect that lasts years.
\cite{jernberg2007long,dethlefsen2008pervasive,jakobsson2010short,dethlefsen2011incomplete}

Substantial attention was given to whether microbial ``types'' exist.
A high-profile paper from Per Bork's group
http://www.nature.com/news/gut-microbial-enterotypes-become-less-clear-cut-1.10276

Important bacteria that were previously unknown?

@@

Major finding: antibiotics.
\cite{dethlefsen2008pervasive,dethlefsen2011incomplete,jakobsson2010short,jernberg2007long}
obesity
turnbaugh papers
http://www.nature.com/nature/journal/v444/n7122/abs/nature05414.html
http://europepmc.org/abstract/MED/18407065/reload=0;jsessionid=Ea4YLfXjd7Cfpx5Hvafq.2
amish study
http://precedings.nature.com/documents/4957/version/1

Data products
reference genomes
HMP DACC.

@@

\cite{ley2006microbial}
Microbial ecology: human gut microbes associated with obesity
Terminology: survey versus metagenome.
definition of a single sample.

@@

There has been a shift from interest in community dynamics to fine-scale interactions between host and immune system.

Trait evolution methods are conspicuously absent.

\cite{wylie2012sequence}
\cite{chen2012associating}
